Analysis of competitive surfing tournaments with generalized Bradley-Terry likelihoods

### 2022-04-24 inst/surfing.Rmd
more work on referee 2

>>>>

# Medina's performance at the Surf Ranch

We will test the null that Medina's performance at the Surf Ranch wa
the same as his performance in the remainder of the tourament.

```{r label=medinaattheranchlike, cache=TRUE}
surfing_wct08     <- hyper2()
surfing_elsewhere <- hyper2()

for(v in o){
   venue <- v[1]
   r <- v[-1]  # first entry is venue

   r <- r[!(r %in% remove)]
   if(length(r)>1){
       if(venue == "wct08"){
           rmod <- r
           rmod[rmod == "Medina"] <- "Medina_wct08"
           surfing_wct08 <- surfing_wct08 + race(rmod)
       } else {
           surfing_elsewhere <- surfing_elsewhere + race(r)
       } 
   }
} # v loop closes	
both_together <- surfing_wct08 + surfing_elsewhere
```

Now test the null that Medina's performance is identical at wct08 and
elsewhere:

```{r, label=testmedinasranchperformance,cache=TRUE}
samep.test(both_together,c("Medina","Medina_wct08"))
```

### 2022-04-24 inst/surfing_jsa.tex
more work on referee 2

>>>>

Medina's performance was startlingly good at Freshwater Pro ({\tt
  wct08}).  Indeed, Medina came first at only two venues (the other
was at Jeffries Bay, South Africa) and it is natural to enquire
whether there is statistical evidence to support the assertion that he
performed better under the more controlled conditions of the Lemoore
Surf Ranch.  To do this, we create an artificial surfer, {\tt
  Medina\_wct08}, who competes at Lemoore, and test the null that {\tt
  Medina} has the same Plackett-Luce strength as {\tt Medina\_wct08}.
We reject this null at a $p$-value of 0.043 and conclude that Medina's
performance at Lemoore is significantly better than his performance at
natural venues.
